---
title: "Developing Data Product Course Project"
author: "ma-haoran"
date: "2021/1/5"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is part of the Developing Data Products Coursera.org course project submission.

It is an R Presentation generated with RStudio.

## What is the purpose of the shiny APP?

The "mtcars" data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles. 

The application build a linear basing on the data, so one could predict mpg onece given cyl, disp and hp.

## How the prediction works?

The regression is a linear model with three variables:
```{r,echo=TRUE,eval=FALSE}
model <- lm(data=mtcars,mpg~as.factor(cyl)+disp+hp)
```

## Ready to give a try?

Use the Shiny App at https://ma-haoran.shinyapps.io/mtcars/

Look up the source code at https://github.com/ma-haoran/presentation/tree/main/regression.model
